### 2019-02-28 manuscript/manuscript.rmd
new pass at blast partition network; relaxed filters for diamond and blast/swissprot results to include more partitions

#### All by all sequence comparison

We used DIAMOND [@Buchfink:2014] to compare each sequence to all others using default `diamond blastp` parameters. We constructed a network with Python and NetworkX [@Hagberg:2008] v2.2 from these results (filters: pident > 95.0, eValue < 1e-25, no self->self) where each node is a sequence and each edge is a result. We extracted each component of connected nodes such that that that every component has no edges to any other nodes.

>>>>

#### Sequence Comparisons

We used DIAMOND [@Buchfink:2014] to compare each sequence to all others using default diamond blastp parameters. We further filtered DIAMOND results such that we retained hits for 90% of partitions (pident > 78.0, eValue < 1e-15, no self->self). We ran BUSCO witrh default parameters for all sequences against the provided metazoa gene set. We also ran a BLAST+ blastp search against the SwissProt [cite] database, filtering hit such that we retain at least one hit for ~97% of partitions (pident > 50.0, eValue < 1e-15).

#### Partition Network

We constructed a network with Python and NetworkX [@Hagberg:2008] v2.2 where each node is a partition and each edge represents a DIAMOND sequence to sequence match. We extracted each component of connected nodes where every component has no edges to any other nodes. We decorated every node with the most numerous SwissProt BLAST+ result and BUSCO results to see which components contain which classes and families of genes.
